\Title

### 2020-02-12 manuscript/manuscript.tex
Add extra lines to figure caption
Improve Green's function section

The fundamental solution $\psi$ \citep[p.~210]{vladimirov1979} of the harmonic
field $V$ must satisfy:

\begin{equation}
    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
        - 4\pi \delta(\mathbf{p}, \mathbf{q})
\end{equation}

@@

Assuming that $\psi$ tends to zero when approaching to infinity as boundary
condition, the fundamental solution of any harmonic field can be obtained as
follows \citep{blakely1995}:

@@

This shows that the Green's function associated with any harmonic field is
equal to the inverse of the Cartesian distance between the evaluation and the
source points.
Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block-median sources. Given a set of observation points (a) we divide
        the survey region on blocks of equal size (b) and compute the median
        location of the observation points that fall inside each block.
        A source point is located beneath each block-median coordinate (c).
    }
    \label{fig:depth-types}
\end{figure*}

>>>>

Considering as boundary condition that $V$ is equal to zero at infinity, then
its fundamental solution $\psi$ (also known as Green's function or radial basis
function) must satisfy \citep[p.~210]{vladimirov1979}:

\begin{equation}
    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
        - 4\pi \delta(\mathbf{p}, \mathbf{q}),
\end{equation}

@@

The fundamental solution of any harmonic field can be obtained as follows
\citep{blakely1995}:

@@

This shows that the Green's function associated with any harmonic field is
equal to the inverse of the Euclidean distance between the evaluation and the
source points.
Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block-median sources. Given a set of observation points (a) we divide
        the survey region on blocks of equal size (b) and compute the median
        location of the observation points that fall inside each block.
        A source point is located beneath each block-median coordinate (c).
        The number of point sources could be less or equal to the number of
        observation points.
        No source is located beneath unpopulated blocks.
    }
    \label{fig:depth-types}
\end{figure*}
